A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies

### 2018-09-02 for_submission/rvaught_2018.tex
update 9/2/18

\documentclass[twocolumn]{aastex61}
\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{graphicx}
\usepackage{amsmath}

@@

\subsection{Image Reduction}
The imaging data were reduced using custom routines written in \emph{Python}. 
The images were first corrected by subtracting and removing the overscan region of the CCD. 
Then the images were bias-subtracted and flat-fielded using twilight flats.
%%% KHRR -- adjusting the following to be different from FAB's words
%To improve the flat-fielding essential for detecting faint extended emission across the %fields, we further correct for the illumination patterns using night-sky flats. The %night-sky flats were produced by combining the unregistered science frames with an %average sigma-clipping algorithm after masking out all the objects, and any bad pixels. 
%%%
An additional flat-fielding correction was performed using night-sky flats to improve our sensitivity to faint extended emission.  The night-sky flats were produced by first masking out all objects and bad pixels in the science frames, and then combining them using an average sigma-clipping algorithm.
Each individual image was cleaned of cosmic rays and bad pixels by utilizing the \emph{L. A. Cosmic} algorithm \citep{Dokkum2001}.
The astrometry solutions were calculated via Astrometry.net \citep{Lang}, and yield a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$. Before image stacking, we ran each frame through \emph{SExtractor} \citeth{Bertin} to create a root mean square (RMS) map of each science image.

@@

\begin{table*}[t]
%\centering
\caption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
determined from analysis of the supplemental Keck/LRIS spectra.}
\begin{tabular}{llllllll} \hline \hline
Object\footnote{ Name in parenthesis to be used as shorthand for the objects throughout the remainder of the paper. } & R.A. & Dec  & $z$ & SFR($M_{\odot}$ yr$^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW$_{\rm{obs}}$(\AA) & $\tau_V$\footnote{ Total V-band optical depth of dust as estimated by SED fitting with MAGPHYS. }\smallskip      \\ \hline 
J033225.26-274524.0 (J.26)      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.539\pm 0.354$ &  $1.227_{-0.20}^{+1.54}$\\

J033231.36-274725.0 (J.36)      & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$5.835 \pm 0.493$ & $1.377_{-0.23}^{+0.60}$\\

J033230.03-274347.3  (J.03)     & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$12.794 \pm 1.710$ & $0.297_{-0.0}^{+0.0}$ \\

J033229.64-274242.6  (J.64)    & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$13.239 \pm 0.263$ & $3.897_{-0.93}^{+1.15}$\\

J033230.57-274518.2  (J.57)    & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ & $1.262_{-0.40}^{+1.23}$ \\
\hline 
\end{tabular}
\tablenotemark{}
\tablenotetext{}{\textit{Note} - The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}}
\label{tab:prop}
\end{table*}

\begin{table}[h!]
\caption{Filter properties  and exposure times of the VLT/FORS2 observations. The widths of the transmission curves ($\Delta\lambda$) are calculated by convolving the transmission curves over the total wavelength range of each filter. These values differ slightly from those reported by the European Southern Observatory. }
\begin{tabular}{llllll} \hline \hline 
Filter & $\lambda_{\rm{eff}}$(\AA)\footnote{$ \lambda_{\rm{eff}}$ is the effective wavelength of the filter transmission curve.} & $\Delta\lambda$(\text{\AA})    & $N$\footnote{ Total number of images.}   & $T(s)$\footnote{ Total exposure time.} & $S$\footnote{ S, the sensitivity of the filter, is in units of $10^{-17}$ ergs counts$^{-1}$ cm$^{-2}$ .}\smallskip  \\ \hline 
HeII+47  & 4675.21 & 50.11 & 38  & 35,959 & 2.45 \\
HeII/3000+48 & 4722.46  & 44.82 & 38 &   36,937 & 2.40  \\ \hline
\end{tabular}
\label{tab:filters}
\end{table}

\subsection{Absolute Flux Calibration}
We acquired observations of the standard star GD50 from archival ESO calibration imaging at 4 independent epochs. Performing aperture photometry at each epoch and airmass, we calculated the atmospheric extinction coefficients, $k$, to be 0.181 magnitudes for the HeII/3000+48 filter and 0.190 magnitudes for the HeII+47 filter. We perform absolute flux calibration using the methods of \cite{Jacoby1987}. We first convolve the spectral energy distribution of the standard star, $F(\lambda)$ in ergs sec$^{-1}$ \AA$^{-1}$ cm$^{-2}$, with that of the known transmission curve of the filter, $T_{i}(\lambda)$. This yields $F_i$, the total observable flux in each bandpass filter $i$ with units of ergs sec$^{-1}$ cm$^{-2}$:
\begin{equation*}
F_{i}=\int F(\lambda)T_{i}(\lambda)d\lambda.
\end{equation*}
It is not uncommon to assume that $F(\lambda)$ is constant over the small width of the filter. 
%However, our filter transmission curves are sampled at $5$\ \AA\ intervals which is the same sampling as the spectral energy distribution of the standard star obtained from the ESO archives (WILL CHECK CALSPEC). 
However, we calculate the integral numerically.
The system sensitivity, including the sensitivity of the telescope optics and the detector response is then given by
\begin{equation*}
S_{i}=\dfrac{F_{i}}{C10^{k_{i}A}},
\end{equation*}\\
where $k_i$ is the extinction in magnitudes per airmass, A is the airmass for each individual exposure, C is the measured count rate of the standard star and $S_i$ is in units of ergs counts$^{-1}$ cm$^{-2}$. Before image co-addition, each science image is corrected for atmospheric extinction by multiplying each frame by $10^{k_{i}A}$. Next, the image is divided by the exposure time, effectively putting the image in units of counts per sec. After co-addition, the images are then multiplied by the appropriate sensitivity factor $S_{i}$. This puts the final images in the appropriate flux units, ergs sec $^{-1}$ cm$^{-2}$.

@@

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.7]{stamps.pdf}
\caption{ $10'' \times 10''$ (or about $70 \rm \ kpc \times 70 \rm \ kpc $) images of each galaxy in our sample. Top row: Continuum surface brightness in ergs s$^{-1}$ cm$^{-2}$ arcsec$^{-2}$ measured in the HeII/3000+48 filter. Bottom row: Continuum-subtracted \ion{Mg}{2} surface brightness.  Absorption can be seen in 4 of 5 galaxies. The red contours represent the outline of the 1$\sigma$ surface brightness limit in the HeII+47 image, defined in Sec. \ref{sec.sb}. The colorbar shows the scaling used for the \ion{Mg}{2} images.}
\label{fig:stamp_images}
\end{figure*}

@@

To calculate the $1\sigma$ SB limit we follow the procedure of \cite{Battaia_2015}. We first mask out all the sources, their associated extended halos, and edge noise in both the HeII+47 and HeII/3000+48 images. We then calculate the RMS of the background in randomly-placed $1\arcsec$ apertures. We convert these RMS values to SB limits per $1~\rm arcsec^2$  aperture. We find that the 1$\sigma$ detection limits 
(SB$_1$) are $6.332\times10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ and $5.808\times10^{-19} $ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ in the HeII/3000+48 and HeII+47 filters, respectively. With the 1$\sigma$ detection limit, SB$_1$, determined for the continuum+\ion{Mg}{2} (HeII+47) image, we define a thicker (or ``extended") annulus to be used to search for any extended \ion{Mg}{2} emission. This extended annulus has an inner radius approximately the size of the SB$_1$ isophotal contour for each galaxy. The outer radius is chosen to be the inner radius plus 5 pixels. The mean radii of these extended apertures are 18, 18, 24 and 21 kpc from the centers of the targets J.26, J.36, J.03 and J.64, respectively. The resulting SB measurements are shown in Figure~\ref{fig:sb_profiles}.

The sensitivity required to detect an extended source depends on its size, as one can reach lower SB levels by spatially averaging over large apertures. In the ideal case of perfect sky subtraction and continuum subtraction, the 1$\sigma$ SB limit for an extended source is $SB_{1}/\sqrt{A_\text{src}}$, where $A_\text{src}$ is the area in arcsec$^2$ and $SB_{1}$ is the surface brightness limit per 1 arcsec$^2$ aperture. In practice, the actual detection limits are affected by systematics from imperfect subtraction. Therefore, we empirically determine the limits as follows. We mask all the artifacts and sources in the continuum-subtracted images. Next, we generate apertures with sizes similar to our extended annulus ($\sim 20 \rm\ sq.arcsec$), place them at random, and extract the fluxes, $F_{\text{src}}$, within these apertures.

 In the ideal case that the sky and continuum are perfectly subtracted the value of $F_{\text{src}}/ \sigma_{\text{src}}$, where $\sigma_{\text{src}} \equiv SB_{1}\sqrt{A_\text{src}}$, from many random apertures should follow a Gaussian distribution with unit variance. The distribution of $F_{\text{src}}/\sigma_{\text{src}}$ for these apertures is shown in Figure \ref{fig:limits}. We calculate the variance and mean of the distribution and find that the variance of the distribution is $\sigma'_{\text{src}}=1.1$, implying that the SB detection limit for our continuum-subtracted image is higher than $\sigma_{\text{src}}$ by a factor of 10\%. We thus adopt $F_{\text{limit}} \equiv \sigma'_{\text{src}}$  as the $1 \sigma$ upper limit on the total line flux of extended \ion{Mg}{2} emission. The SB$_{\text{limit}}$ is then $F_{\text{limit}}/A_{\rm{src}}$. The values of $F_{\text{src}}$ and 5SB$_{\text{limit}}$ for each galaxy are listed in Table \ref{tab:det_lims}.

@@

\begin{table}[h]
\centering
%\begin{minipage}{4in}
\caption{Significance of extracted flux and detection limits.\label{tab:det_lims}}  
\begin{tabular}{lllll} \hline \hline
Object & F$_{\rm{src}}$(\ion{Mg}{2})\footnote{ \ion{Mg}{2} flux is in units of $10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$. The value in parentheses is the statistical significance with respect to $\sigma_{\text{src}}$. } & 5SB$_{\text{limit}}$\footnote{ Limits are in units of $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^{-2}$.} & Area\footnote{ Area of the extended annulus in arcsec$^2$.} \\  \hline
J033225.26-274524.0 &  2.44(0.92)& 6.51	& 21 \\
J033232.36-274725.0 &  -1.40(-0.53)& 6.51 & 21 \\
J033230.03-274347.3 &  -5.23(-1.75)& 5.74 & 27 \\
J033229.64-274242.5 &  1.23 (0.44) & 6.22  &26 \\
J033230.57-274518.2 &  -2.53 (-1.00) & 6.81 &18 \\ \hline
\end{tabular}
%\end{minipage}
\end{table}

\subsection{Test of Surface Brightness Limits}\label{subsec:test}
To show that our detection limits are reasonable, we simulate emission with varying intensities. The results of this exercise are shown in Figure \ref{fig:sigmas}. For each galaxy, we assign our simulated emission a constant surface brightness corresponding to 1, 3, 5, 10 and 20 times the $1\sigma$ SB$_{\text{limit}}$ inside the largest annulus used (i.e., the extended annulus). Additionally, we assume Gaussian noise with 1$\sigma$ equal to 1SB$_{\text{limit}}$. After placing the simulated emission around the galaxy, we subtract the continuum in the same manner as explained in Section \ref{subsec.cont_sub}.

We then construct a smoothed $\chi$ image following the techniques in \cite{Hennawi2013} and \cite{Battaia_2015}. First, we smooth the continuum-subtracted image:

\begin{equation}
I_{\text{smooth}}= \text{CONVOLVE[NB-CONTINUUM]},
\end{equation}
where the CONVOLVE operation indicates convolution of the images with a Gaussian kernel with FWHM=1.5 pixels. Next, we computed the sigma image ($\sigma_{\text{smooth}}$) for the smoothed image ($I_{\text{smooth}}$) by propagating the noise image of the unsmoothed data:
\begin{equation}
\sigma_{\text{smooth}}=\sqrt{\text{CONVOLVE}^2[\sigma^2_{\text{unsmooth}}]},
\end{equation}
where the CONVOLVE$^2$ operation indicates the convolution of the variance image with the square of the Gaussian kernel. The smoothed $\chi$ image is then
\begin{equation}
\chi_{\text{smooth}}=\frac{I_{\text{smooth}}}{\sigma_{\text{smooth}}}.
\end{equation}
This $\chi_{\text{smooth}}$ image aids in recognizing the presence of extended \ion{Mg}{2} emission.

@@

\subsection{Limits on \ion{Mg}{2} Emission}
For our sample of galaxies, we are sensitive to extended emission in annuli at %minimum 
projected distances of 
18, 18, 24 and 21 kpc from the centers of J.26, J.36, J.03 and J.64, respectively.
%%% KHRR -- don't understand these distances
 We do not detect any significant \ion{Mg}{2} emission at these distances around any of our target galaxies. The $\chi_{\text{smooth}}$ images shown in Figure \ref{fig:sigmas} confirm this. A comparison of the simulated emission with the $\chi_{\text{smooth}}$ version of the original continuum-subtracted image, shown in the first column, similarly suggests that we do not detect any extended \ion{Mg}{2} emission. We thus place $5\sigma$ upper limits on the SB of \ion{Mg}{2} emission for each galaxy in the sample, summarized in Table \ref{tab:det_lims}. The most sensitive detection limit using the largest area is SB(\ion{Mg}{2}) $<$ 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^{-2}$, computed for the galaxy J.03.

@@

%Figure \ref{fig:SFR_lim} shows a plot of the 5$\sigma$ detection limits determined for each galaxy in our sample as well as the SB calculated for the galaxy TKRS 4389 vs. SFR. The figure suggests that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389 in our narrowband imaging. Taken at face value, the figure could be consistent with a positive correlation between \ion{Mg}{2} SB and SFR. Future observations are needed to verify this trend, and the possibility that objects with yet higher SFRs ($>\sim$50 $\msunperyr$) exhibit brighter \ion{Mg}{2} emission. Figure \ref{fig:detection_lim} shows the same SB values as in Figure \ref{fig:SFR_lim} vs. $\log(M_*/M_{\odot})$. The figure suggests that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies. Both \cite{Erb2012} and \cite{Feltre2018} observed a similar trend in their examination of the total \ion{Mg}{2} emission strength vs. galaxy $M_*$. Combining the previous figures, Figure \ref{fig:sSFR_lim} shows that the galaxy with detected \ion{Mg}{2} also has the highest specific SFR (SFR/$M_*$). If it is ultimately confirmed that low-$M_*$ galaxies with the highest SFRs exhibit the brightest emission this could point to a physical link between the escape velocity of galaxies and the spatial extent of wind material.

@@

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.7]{ew_comb.pdf}
\caption{Radial profile of the mean EW of \ion{Mg}{2} absorption for four of our sample galaxies. Profiles for J.26,  J.36,  J.03, and J.64 are shown with blue points, green squares, red circles, and cyan stars, respectively. The mean EW values are the same as those shown in the right column of Figure \ref{fig:ews}. We have normalized the corresponding radii by the approximate size of the SB$_1$ contour of each galaxy. There is significant scatter relative to the error bars at extended distances.}
\label{fig:ew_comb}
\end{figure*}

>>>>

\documentclass[twocolumn]{aastex62}
\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{graphicx}
\usepackage{amsmath}

@@

\subsection{Image Reduction}
The imaging data were fully reduced using custom routines written in \emph{Python}. 
The images were first corrected by subtracting and removing the overscan region of the CCD. 
Then the images were bias-subtracted and flat-fielded using twilight flats.
%%% KHRR -- adjusting the following to be different from FAB's words
%To improve the flat-fielding essential for detecting faint extended emission across the %fields, we further correct for the illumination patterns using night-sky flats. The %night-sky flats were produced by combining the unregistered science frames with an %average sigma-clipping algorithm after masking out all the objects, and any bad pixels. 
%%%
An additional flat-fielding correction was performed using night-sky flats to improve our sensitivity to faint extended emission.  The night-sky flats were produced by first masking out all objects and bad pixels in the science frames, and then combining them using an average sigma-clipping algorithm.
Cosmic rays and bad pixels in the science images are removed by utilizing the \emph{L. A. Cosmic} algorithm \citep{Dokkum2001}.
The astrometry solutions were calculated via Astrometry.net \citep{Lang}, and yield a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$. Before image stacking, we ran each frame through \emph{SExtractor} \citeth{Bertin} to create a root mean square (RMS) map of each science image.

@@

%\begin{table*}[t]
%\centering
%\caption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
%determined from analysis of the supplemental Keck/LRIS spectra.}
%\begin{tabular}{llllllll} \hline \hline
%Object\footnote{ Name in parenthesis to be used as shorthand for the objects throughout the remainder of the paper. } & R.A. & Dec  & $z$ & SFR($M_{\odot}$ yr$^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW$_{\rm{obs}}$(\AA) & $\tau_V$\footnote{ Total V-band optical depth of dust as estimated by SED fitting with MAGPHYS. }\smallskip      \\ \hline 
%J033225.26-274524.0 (J.26)      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.539\pm 0.354$ &  $1.227_{-0.20}^{+1.54}$\\

%J033231.36-274725.0 (J.36)      & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$5.835 \pm 0.493$ & $1.377_{-0.23}^{+0.60}$\\

%J033230.03-274347.3  (J.03)     & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$12.794 \pm 1.710$ & $0.297_{-0.0}^{+0.0}$ \\

%J033229.64-274242.6  (J.64)    & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$13.239 \pm 0.263$ & $3.897_{-0.93}^{+1.15}$\\

%J033230.57-274518.2  (J.57)    & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ & $1.262_{-0.40}^{+1.23}$ \\
%\hline 
%\end{tabular}
%\tablenotemark{}
%\tablenotetext{}{\textit{Note} - The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}}
%\label{tab:prop}
%\end{table*}

\begin{deluxetable*}{c c c c D D c D}
\tablecaption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
determined from analysis of the supplemental Keck/LRIS spectra. \label{tab:prop}}
\tablehead{\colhead{Object} & \colhead{R.A.} & \colhead{Dec} & \colhead{$z$} & \multicolumn2c{SFR} & \multicolumn2c{$\log{M}$} & \colhead{EW$_{\rm{obs}}$} & \multicolumn2c{ $\tau_V$} \\ 
\colhead {} & \colhead {} & \colhead {} & \colhead{} & \multicolumn2c{($M_{\odot}$ yr$^{-1}$)} & \multicolumn2c{$\log{M_{*}/M_{\odot}}$} & \colhead{(\AA)} & \multicolumn2c{}}
\decimals
\startdata
J033225.26-274524.0 (J.26)     & 03:32:25.26 & -27:45:23.9  &   0.6660  & $9.1_{-3.7}^{+1.3}$     & $9.86_{-0.04}^{+0.05}$   & \ $7.539\pm 0.354$   &  $1.227_{-0.20}^{+1.54}$ \\ 
J033231.36-274725.0 (J.36)     & 03:32:31.35 & -27:47:24.9  &   0.6669  & $10.5_{-1.6}^{+1.7}$   & $10.02_{-0.03}^{+0.03}$ & \ $5.835 \pm 0.493$   & $1.377_{-0.23}^{+0.60}$ \\
J033230.03-274347.3 (J.03)     & 03:32:30.03 & -27:43:47.2  &   0.6679  & $3.8_{-0}^{+0}$           & $10.98_{-0.0}^{+0.01}$   & $12.794 \pm 1.710$ & $0.297_{-0.0}^{+0.0}$ \\
J033229.64-274242.6 (J.64)     & 03:32:29.64 & -27:42:42.5  &   0.6671  & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ & $13.239 \pm 0.263$ & $3.897_{-0.93}^{+1.15}$ \\
J033230.57-274518.2 (J.57)     & 03:32:30.56 & -27:45:18.2  &   0.6807  & $12.6_{-2.1}^{+1.7}$   & $10.48_{-0.07}^{+0.03}$ & \ $6.106 \pm 0.370$   & $1.262_{-0.40}^{+1.23}$ \\
\enddata
\tablecomments{The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}}
\end{deluxetable*}

\begin{deluxetable}{c c c c c c}
\tablecaption{Filter properties  and exposure times of the VLT/FORS2 observations. The widths of the transmission curves ($\Delta\lambda$) are calculated by convolving the transmission curves over the total wavelength range of each filter. These values differ slightly from those reported by the European Southern Observatory. \label{tab:filters}}
\tablehead{\colhead {Filter (Line)} & \colhead {$\lambda_{\rm{eff}}$\tablenotemark{a}} & \colhead {$\Delta\lambda$\tablenotemark{b}} & \colhead {N\tablenotemark{c}} & \colhead{$T$\tablenotemark{d}} & \colhead{$S$\tablenotemark{e}} \\
\colhead {} & \colhead{(\AA)} & \colhead{(\AA)} & \colhead{} & \colhead{(S)} & \colhead{}}
\startdata
HeII+47 (\ion{Mg}{2})         & 4675.21  & 50.11 & 38  & 35,959 & 2.45 \\
HeII/3000+48 (Cont.) & 4722.46  & 44.82 & 38  & 36,937 & 2.40  \\
\enddata
\tablenotetext{a}{$ \lambda_{\rm{eff}}$ is the effective wavelength of the filter transmission curve.}
\tablenotetext{b}{FWHM of the filter.}
\tablenotetext{c}{Total number of images.}
\tablenotetext{d}{Total exposure time.}
\tablenotetext{e}{S, the sensitivity of the filter, is in units of $10^{-17}$ ergs counts$^{-1}$ cm$^{-2}$.}
\end{deluxetable}

\subsection{Absolute Flux Calibration}
We acquired observations of the standard star GD50 from archival ESO calibration imaging at 4 independent epochs. Performing aperture photometry at each epoch and airmass, we calculated the atmospheric extinction coefficients, $k$, to be 0.181 magnitudes for the HeII/3000+48 filter and 0.190 magnitudes for the HeII+47 filter. We perform absolute flux calibration using the methods of \cite{Jacoby1987}. We first convolve the spectral energy distribution of the standard star, $F(\lambda)$ in ergs sec$^{-1}$ \AA$^{-1}$ cm$^{-2}$, with that of the known transmission curve of the filter, $T_{i}(\lambda)$. This yields $F_i$, the total observable flux in each bandpass filter $i$ with units of ergs sec$^{-1}$ cm$^{-2}$:
\begin{equation*}
F_{i}=\int F(\lambda)T_{i}(\lambda)d\lambda.
\end{equation*}
It is not uncommon to assume that $F(\lambda)$ is constant over the small width of the filter. 
However, since our filter transmission curves are sampled at wavelengths similar to sampling of the spectrum of GD50 from the the CALSPEC library \citep{Bohlin2017}, we interpolate both spectra and compute the integral numerically. 
The conversion from count rate to flux units for each filter is then given by
\begin{equation*}
S_{i}=\dfrac{F_{i}}{C10^{k_{i}A}},
\end{equation*}\\
where $k_i$ is the extinction in magnitudes per airmass, A is the airmass for each individual exposure, C is the measured count rate of the standard star and $S_i$ is in units of ergs counts$^{-1}$ cm$^{-2}$. Before image co-addition, each science image is corrected for atmospheric extinction by multiplying each frame by $10^{k_{i}A}$. Next, the image is divided by the exposure time, effectively putting the image in units of counts per sec. After co-addition, the images are then multiplied by the appropriate sensitivity factor $S_{i}$. This puts the final images in the appropriate flux units, ergs sec $^{-1}$ cm$^{-2}$.

@@

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.7]{stamps.pdf}
\caption{ $10'' \times 10''$ (or about $70 \rm \ kpc \times 70 \rm \ kpc $) images of each galaxy in our sample. Top row: Continuum surface brightness in ergs s$^{-1}$ cm$^{-2}$ pixel, measured in the HeII/3000+48 filter. Bottom row: Continuum-subtracted \ion{Mg}{2} surface brightness.  Absorption can be seen in 4 of 5 galaxies. The red contours represent the outline of the 1$\sigma$ surface brightness limit in the HeII+47 image, defined in Sec. \ref{sec.sb}. The colorbar shows the scaling used for the bottom row \ion{Mg}{2} images.}
\label{fig:stamp_images}
\end{figure*}

@@

To calculate the $1\sigma$ SB limit we follow the procedure of \cite{Battaia_2015}. We first mask out all the sources, their associated extended halos, and edge noise in both the HeII+47 and HeII/3000+48 images. We then calculate the RMS of the background in randomly-placed $1\arcsec$ apertures. We convert these RMS values to SB limits per $1~\rm arcsec^2$  aperture. We find that the 1$\sigma$ detection limits 
(SB$_1$) are $6.332\times10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ and $5.808\times10^{-19} $ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ in the HeII/3000+48 and HeII+47 filters, respectively. With the 1$\sigma$ detection limit, SB$_1$, determined for the continuum+\ion{Mg}{2} (HeII+47) image, we define a thicker (or ``extended") annulus to be used to search for any extended \ion{Mg}{2} emission. This annulus will have an inner radius approximately the size of the SB$_1$ isophotal contour for each galaxy. The outer radius is chosen to be the inner radius plus 5 pixels. With this larger annulus, we can average any flux over large areas to reach lower SB. The mean radii of these extended apertures are 18, 18, 24 and 21 kpc from the centers of the targets J.26, J.36, J.03 and J.64, respectively. The resulting SB measurements are shown in Figure~\ref{fig:sb_profiles}.

In the case of perfect sky subtraction and continuum subtraction, the 1$\sigma$ SB limit for an extended source is $SB_{1}/\sqrt{A_\text{src}}$, where $A_\text{src}$ is the area in arcsec$^2$ and $SB_{1}$ is the surface brightness limit per 1 arcsec$^2$ aperture. However, our actual detection limits are altered by systematic error from imperfect subtraction. Therefore, we determine the limits as follows. We first mask all the artifacts and sources in the continuum-subtracted images. Next, we generate many apertures with sizes similar to our extended annulus ($\sim 20 \rm\ sq.arcsec$), place them at random, and extract the fluxes, $F_{\text{src}}$, within these apertures. We then normalize the vales of $F_{\text{src}}$ by dividing by $\sigma_{\text{src}}$, where $\sigma_{\text{src}} \equiv SB_{1}\sqrt{A_\text{src}}$. For perfect sky subtraction and continuum subtraction, the distribution of extracted fluxes should follow a Gaussian distribution with a variance equal to $\sigma_{\text{src}}$. The distribution of $F_{\text{src}}/\sigma_{\text{src}}$ for these apertures is shown in Figure \ref{fig:limits}

We calculate the variance and mean of the distribution and find that the variance of the distribution is $\sigma'_{\text{src}}=1.1$, implying that the SB detection limit for our continuum-subtracted image is higher than $\sigma_{\text{src}}$ by a factor of 10\%. We adopt $F_{\text{limit}} \equiv \sigma'_{\text{src}}$  as the $1 \sigma$ upper limit on the total line flux of extended \ion{Mg}{2} emission. The SB$_{\text{limit}}$ is then $F_{\text{limit}}/A_{\rm{src}}$. The values of $F_{\text{src}}$ and 5SB$_{\text{limit}}$ for each galaxy are listed in Table \ref{tab:det_lims}.

@@

\begin{deluxetable}{c D c c}
\tablecaption{Significance of extracted flux and detection limits.\label{tab:det_lims}}
\tablehead{\colhead {Object } & \multicolumn2c{F$_{\rm{src}}$(\ion{Mg}{2})\tablenotemark{a}} & \colhead {5SB$_{\text{limit}}$\tablenotemark{b}} & \colhead {Area\tablenotemark{c}}}
\decimals
\startdata
J033225.26-274524.0 &   2.44(0.92)   & 6.51 & 21 \\
J033232.36-274725.0 &  -1.40(-0.53)  & 6.51 & 21 \\
J033230.03-274347.3 &  -5.23(-1.75)  & 5.74 & 27 \\
J033229.64-274242.5 &   1.23 (0.44)  & 6.22 & 26 \\
J033230.57-274518.2 &  -2.53 (-1.00) & 6.81 &18 \\
\enddata
\tablenotetext{a}{\ion{Mg}{2} flux is in units of $10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$. The value in parentheses is the statistical significance with respect to $\sigma_{\text{src}}$.}
\tablenotetext{b}{Limits are in units of $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^{-2}$.}
\tablenotetext{c}{Area of the extended annulus in arcsec$^2$.}
\end{deluxetable}

\subsection{Test of Surface Brightness Limits}\label{subsec:test}
To show that \ion{Mg}{2} emission with SB strengths comparable to our limits can be detected in our narrowband imaging, we simulate emission with varying intensities of SB$_{\text{limit}}$. For each galaxy, we assign our simulated emission a constant surface brightness corresponding to 1, 3, 5, 10 and 20 times the $1\sigma$ SB$_{\text{limit}}$ inside the largest annulus used (i.e., the extended annulus). We assume Gaussian noise with 1$\sigma$ equal to 1SB$_{\text{limit}}$. Next, we subtract the continuum in the same manner as explained in Section \ref{subsec.cont_sub}.

We construct smoothed $\chi$ images, $\chi_{\text{smooth}}$, for each level of simulated emission, following the techniques in \cite{Hennawi2013} and \cite{Battaia_2015}. These $\chi_{\text{smooth}}$ images can aid in identifying the presence and detectability of extended \ion{Mg}{2} emission.

First, the model continuum-subtracted image is smoothed by the operation:
\begin{equation}
I_{\text{smooth}}= \text{CONVOLVE[line-continuum]},
\end{equation}
where the CONVOLVE operation indicates convolution of the \ion{Mg}{2} images with a Gaussian kernel with FWHM=1.5 pixels. Next, we computed the sigma image, $\sigma_{\text{smooth}}$, by convolving the propagated error image:
\begin{equation}
\sigma_{\text{smooth}}=\sqrt{\text{CONVOLVE}^2[\sigma^2]},
\end{equation}
where the CONVOLVE$^2$ operation indicates convolution of the image with the square of the Gaussian kernel. The smoothed $\chi$ image is then the product of the data image divided by the sigma image.
\begin{equation}
\chi_{\text{smooth}}=\frac{I_{\text{smooth}}}{\sigma_{\text{smooth}}}.
\end{equation}

@@

\subsection{Limits on \ion{Mg}{2} Emission}
For our sample of galaxies, we are sensitive to extended emission in annuli at projected distances of 18, 18, 24 and 14 kpc from the centers of J.26, J.36, J.03 and J.64, respectively.
%%% KHRR -- don't understand these distances
 We do not detect any significant \ion{Mg}{2} emission at these distances around any of our target galaxies. The $\chi_{\text{smooth}}$ images shown in Figure \ref{fig:sigmas} confirm this. A comparison of the simulated emission with the $\chi_{\text{smooth}}$ version of the original continuum-subtracted image, shown in the first column, similarly suggests that we do not detect any extended \ion{Mg}{2} emission. We thus place $5\sigma$ upper limits on the SB of \ion{Mg}{2} emission for each galaxy in the sample, summarized in Table \ref{tab:det_lims}. The most sensitive detection limit using the largest area is SB(\ion{Mg}{2}) $<$ 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^{-2}$, computed for the galaxy J.03.

@@

@@

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.7]{ew_comb.pdf}
\caption{Radial profile of the mean EW of \ion{Mg}{2} absorption for four of our sample galaxies. Profiles for J.26,  J.36,  J.03, and J.64 are shown with blue points, green squares, red circles, and cyan stars, respectively. The mean EW values are the same as those shown in the right column of Figure \ref{fig:ews}. We have normalized the corresponding radii by the approximate size of the SB$_1$ contour of each galaxy.}
\label{fig:ew_comb}
\end{figure*}
